\LARGE \bf Reactive Trajectory Planning and Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-04-20 root.tex
small sentence addition in section 4 for clarity
figures at top and bottom only

\begin{figure}[tb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=0.8\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=0.9\columnwidth]{graphics/RSTOP_Replan.png}}
  \\
  \subfigure[PSTOP diagram showing bounds for reverting to NORMAL mode.]{\includegraphics[width=0.7\columnwidth]{graphics/RSTOP_Resume.png}}
  \caption{Graphical representation of static and dynamic thresholds used to trigger state transitions.}
  \label{fig:react}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \subfigure[
    The result of dividing a single sub-path into separate segments.
    The clustering algorithm used here sets segments boundaries before and after curves.
    The sub-path segments in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.1 m/s (25 mi/hr).
  ]{
  \label{fig:1Dto2DandSegmentationa}
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  \subfigure[
    An example of how the sub-path's segment boundaries are determined, as well as how $v_m$ is consolidated to determine the speed ceiling for each segment.
    The x-axis corresponds to distance along the subpath above.
    The legal speed limit of 11.1 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling ($v_m$) is shown in blue.
  ]{
  \label{fig:1Dto2DandSegmentationb}
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  }
  \caption{Dividing a subpath into segments and determining speed ceilings for each segment.}
  \label{fig:1Dto2DandSegmentation}
\end{figure}

@@

Now appropriate values of $a_m^-$ and $j_m^-$ must be chosen to completely parameterize the trajectory.
For calculating $\Delta s_{RSTOP}$, the same set of values from normal planning is used and the distance traversed in the resultant trajectory is reported as the current value of $\Delta s_{RSTOP}$.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.65\columnwidth]{graphics/PathProjectionSlice.png}
  \caption{Showing projection of the current position of the car shown by green triangle to s coordinate system. Each circle represents a node, and the lines between them are links. The orange dots indicate future trajectory samples which are sent to the controller.
  }

>>>>

\begin{figure}[tb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=0.75\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=0.85\columnwidth]{graphics/RSTOP_Replan.png}}
  \\
  \subfigure[PSTOP diagram showing bounds for reverting to NORMAL mode.]{\includegraphics[width=0.7\columnwidth]{graphics/RSTOP_Resume.png}}
  \caption{Graphical representation of static and dynamic thresholds used to trigger state transitions.}
  \label{fig:react}
\end{figure}

@@

\begin{figure}[tb]
  \centering
  \subfigure[
    The result of dividing a single sub-path into separate segments.
    The clustering algorithm used here sets segments boundaries before and after curves.
    The sub-path segments in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.1 m/s (25 mi/hr).
  ]{
  \label{fig:1Dto2DandSegmentationa}
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  \subfigure[
    An example of how the sub-path's segment boundaries are determined, as well as how $v_m$ is consolidated to determine the speed ceiling for each segment.
    The x-axis corresponds to distance along the subpath above.
    The legal speed limit of 11.1 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling ($v_m$) is shown in blue.
  ]{
  \label{fig:1Dto2DandSegmentationb}
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  }
  \caption{Dividing a subpath into segments and determining speed ceilings for each segment.}
  \label{fig:1Dto2DandSegmentation}
\end{figure}

@@

Now appropriate values of $a_m^-$ and $j_m^-$ must be chosen to completely parameterize the trajectory.
For calculating $\Delta s_{RSTOP}$, the same set of values from normal planning is used and the distance traversed in the resultant trajectory is reported as the current value of $\Delta s_{RSTOP}$. This is the procedure for computing the dynamic, speed-dependent distance required to stop at any epoch.

@@

\begin{figure}[tb]
  \centering
  \includegraphics[width=0.65\columnwidth]{graphics/PathProjectionSlice.png}
  \caption{Showing projection of the current position of the car shown by green triangle to s coordinate system. Each circle represents a node, and the lines between them are links. The orange dots indicate future trajectory samples which are sent to the controller.
  }
